Distributed Environment for Auctioning Virtual Power System Resources

### 2022-02-04 other/paper-aicts-chekan.tex
chekan: added M's contacts, fixed a header and access dates

%%
%% The "title" command
\title{Distributed Environment for Auctioning Virtual Power System Resources}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1,2]{Mikhail A. Chekan}[%
orcid=0000-0003-2428-2471,
email=eugeneai@icc.ru,
url=https://github.org/eugeneai,
]
\author[1,2]{Evgeny A. Cherkashin}[%
orcid=0000-0003-2428-2471,
email=eugeneai@icc.ru,
url=https://github.org/eugeneai,
]
\address[1]{Matrosov Institute for System Dynamics and Control Theory of Siberian Branch of Russian Academy of Sciences, 134 Lermontov St, Irkutsk, 664033, Russian Federation}

@@

Game model (перевести картинку)

@@

   \bibitem{b1} Business for society: how Siemens is changing life in Russia. Smart Energy. RBC, 2016 (in Russian). URL:\url{http://siemens.rbc.ru/article1.html} (access date: 05-15-2021)
   \bibitem{b2} E.~B.~Makarov. Game forms of education. Open lesson. (in Russian) URL:\url{https://openlesson.rf/articles/556327/} (access date: 05-15-2021)
   \bibitem{b3} Intelligent energy systems. Stand-simulator for programming and management of urban power networks. (in Russian) URL:\url{http://polyus-nt.ru/powerstand.html} (access date: 11/22/2021).

@@

   \bibitem{b9} gRPC. URL:\url{https://grpc.io} (access date: 05-15-2021)
   \bibitem{b10} OAuth Community Site. URL:\url{https://oauth.net} (access date: 05-15-2021)
   \bibitem{b11} ORY Oathkeeper. GitHub. URL:\url{https://github.com/ory/oathkeeper} (access date: 05-15-2021)

@@

   \bibitem{b13} A.~Skorodumov. Secure access to the company's information resources.  Information Security No.~2. URL:\url{http://lib.itsec.ru/articles2/sys_ogr_dost/bezopasnyy-dostup-k-informatsionnym-resursam-kompanii} (access date: 05-15-2021)
   \bibitem{b14} SSH Tunnel. URL:\url{https://www.ssh.com/ssh/ tunneling/} (access date: 05-15-2021)
   \bibitem{b15} Users. OpenSSH URL:\url{https://www.openssh.com/users.html} (access date: 05-15-2021)
   \bibitem{b16} NTO (in Russian) URL:\url{https://nti-contest.ru/} (access date: 05-20-2021)
   \bibitem{b17} Educational intensive ``Island 10-21''. Information Bureau 20.35. (in Russian) URL:\url{https://ntinews.ru/event/obrazovatelnyy-intensiv-ostrov-10-21.html} (access date: 05-20-2021)

@@

   \bibitem{b20} RFC 6455 — The WebSocket Protocol. IETF. URL:\url{https://tools.ietf.org/html/rfc6455} (access date: 05-20-2021)
   \bibitem{b21} Concise Binary Object Representation. URL:\url{https://cbor.io/} (access date: 20.05.2021)
   \bibitem{b22} Comparison of JSON Like Serializations. URL:\url{http://zderadicka.eu/comparison-of-json-like-serializations-json-vs-ubjson-vs-messagepack-vs-cbor/} (access date: 21.05.2021)
   \bibitem{b23} NixOS Linux. URL:\url{https://nixos.org/} (access date: 05-15-2021)

@@

   \bibitem{b25} Haskell Language. URL:\url{https://haskell.org} (access date: 20.05.2021)
   \bibitem{b26} Theh Dhall configuration language. URL:\url{https://dhall-lang.org/} (access date: 21.05.2021)
   \bibitem{b27} Bid Wars // Google Play [Электронный ресурс]. 2021. URL:\url{https://play.google.com/store/apps/details?id=br.com.tapps.bidwars} (access date: 05-15-2021)
   \bibitem{b28} TimeZero. MMORPG Handbook. Auction. (in Russian) URLs:\url{http://web.archive.org/web/20160325215014/}, \url{https://www.timezero.ru/manual/auction.ru.html} (access date: 05-15-2021)
   \bibitem{b29} Sberbank-AST (in Russian) URL:\url{http://www.sberbank-ast.ru/purchaseList.aspx} (access date: 05-15-2021)
   \bibitem{b30} O.~Titz. Why TCP Over TCP Is A Bad Idea. URL:\url{http://sites.inka.de/bigred/devel/tcp-tcp.html} (access date: 21.05.2021)
   \bibitem{b31} C.~Rapier et al. High performance SSH. SCP-HPN-SSH URL:\url{http://www.psc.edu/networking/projects/hpn-ssh} (access date: 21.05.2021)

@@

   \bibitem{b33} S.~Hobbs. CORS Tutorial: A Guide to Cross-Origin Resource Sharing. Auth0. URL:\url{https://auth0.com/blog/cors-tutorial-a-guide-to-cross-origin-resource-sharing/} (access date: 21.05.2021)

>>>>

%%
%% The "title" command
\title{Distributed Environment for Auctioning Virtual Power System Resources}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1,2]{Mikhail A. Chekan}[%
orcid=0000-0001-7622-421X,
email=chekoopa@mail.ru,
url=https://github.org/chekoopa,
]
\author[1,2]{Evgeny A. Cherkashin}[%
orcid=0000-0003-2428-2471,
email=eugeneai@icc.ru,
url=https://github.org/eugeneai,
]
\address[1]{Matrosov Institute for System Dynamics and Control Theory of Siberian Branch of Russian Academy of Sciences, 134 Lermontov St, Irkutsk, 664033, Russian Federation}

@@

\section{Game model}
\label{sec:gamemodel}

@@

   \bibitem{b1} Business for society: how Siemens is changing life in Russia. Smart Energy. RBC, 2016 (in Russian). URL:\url{http://siemens.rbc.ru/article1.html} (access date: 11-22-2021)
   \bibitem{b2} E.~B.~Makarov. Game forms of education. Open lesson. (in Russian) URL:\url{https://urok.1sept.ru/articles/556327/} (access date: 11-22-2021)
   \bibitem{b3} Intelligent energy systems. Stand-simulator for programming and management of urban power networks. (in Russian) URL:\url{http://polyus-nt.ru/powerstand.html} (access date: 11-22-2021).

@@

   \bibitem{b9} gRPC. URL:\url{https://grpc.io} (access date: 11-22-2021)
   \bibitem{b10} OAuth Community Site. URL:\url{https://oauth.net} (access date: 11-22-2021)
   \bibitem{b11} ORY Oathkeeper. GitHub. URL:\url{https://github.com/ory/oathkeeper} (access date: 11-22-2021)

@@

   \bibitem{b13} A.~Skorodumov. Secure access to the company's information resources.  Information Security No.~2. URL:\url{http://lib.itsec.ru/articles2/sys_ogr_dost/bezopasnyy-dostup-k-informatsionnym-resursam-kompanii} (access date: 11-22-2021)
   \bibitem{b14} SSH Tunnel. URL:\url{https://www.ssh.com/ssh/ tunneling/} (access date: 11-22-2021)
   \bibitem{b15} Users. OpenSSH URL:\url{https://www.openssh.com/users.html} (access date: 11-22-2021)
   \bibitem{b16} NTO (in Russian) URL:\url{https://ntcontest.ru/} (access date: 11-22-2021)
   \bibitem{b17} Educational intensive ``Island 10-21''. Information Bureau 20.35. (in Russian) URL:\url{https://ntinews.ru/event/obrazovatelnyy-intensiv-ostrov-10-21.html} (access date: 11-22-2021)

@@

   \bibitem{b20} RFC 6455 — The WebSocket Protocol. IETF. URL:\url{https://tools.ietf.org/html/rfc6455} (access date: 12-22-2021)
   \bibitem{b21} Concise Binary Object Representation. URL:\url{https://cbor.io/} (access date: 11-22-2021)
   \bibitem{b22} Comparison of JSON Like Serializations. URL:\url{http://zderadicka.eu/comparison-of-json-like-serializations-json-vs-ubjson-vs-messagepack-vs-cbor/} (access date: 11-22-2021)
   \bibitem{b23} NixOS Linux. URL:\url{https://nixos.org/} (access date: 11-22-2021)

@@

   \bibitem{b25} Haskell Language. URL:\url{https://haskell.org} (access date: 11-22-2021)
   \bibitem{b26} Theh Dhall configuration language. URL:\url{https://dhall-lang.org/} (access date: 11-22-2021)
	\bibitem{b27} Bid Wars // Google Play [Электронный ресурс]. 2021. URL:\url{https://play.google.com/store/apps/details?id=br.com.tapps.bidwars} (access date: 11-22-2021)
   \bibitem{b28} TimeZero. MMORPG Handbook. Auction. (in Russian) URLs:\url{http://web.archive.org/web/20160325215014/}, \url{https://www.timezero.ru/manual/auction.ru.html} (access date: 11-22-2021)
   \bibitem{b29} Sberbank-AST (in Russian) URL:\url{http://www.sberbank-ast.ru/purchaseList.aspx} (access date: 11-22-2021)
   \bibitem{b30} O.~Titz. Why TCP Over TCP Is A Bad Idea. URL:\url{http://sites.inka.de/bigred/devel/tcp-tcp.html} (access date: 11-22-2021)
   \bibitem{b31} C.~Rapier et al. High performance SSH. SCP-HPN-SSH URL:\url{http://www.psc.edu/networking/projects/hpn-ssh} (access date: 11-22-2021)

@@

   \bibitem{b33} S.~Hobbs. CORS Tutorial: A Guide to Cross-Origin Resource Sharing. Auth0. URL:\url{https://auth0.com/blog/cors-tutorial-a-guide-to-cross-origin-resource-sharing/} (access date: 11-22-2021)
